Enhancement of SDR in Thessaloniki

### 2024-04-11 high_aod/GHI_enh_02_ID_CE_.tex
Commit 2024-04-11 14:14

\begin{verbatim}
Warning:

 ** Test is active!! ** 
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.30}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

@@

\begin{verbatim}
 [1]        NA        NA 1.0857621 0.9949418 0.9171711 0.8498384 0.7909847
 [8] 0.7391123 0.6930560 0.6518963 0.6148972
\end{verbatim}

@@

\begin{verbatim}
C4 factor: 1.1 
\end{verbatim}

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6054123 & 148044 \\
\end{longtable}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-191} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-192} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-193} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-194} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-195} \end{center}

@@

\begin{verbatim}
Warning: TEST IS ACTIVE !!
\end{verbatim}

TEST IS ACTIVE !!

@@

\begin{verbatim}
2024-04-11 09:13:59.5 athan@sagan GHI_enh_02_ID_CE_highAOD.R 0.935513 mins
\end{verbatim}

>>>>

@@

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.11}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.31}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

@@

\begin{verbatim}
 [1]        NA        NA 1.0941141 1.0026612 0.9243490 0.8565476 0.7972846
 [8] 0.7450515 0.6986754 0.6572300 0.6199744
\end{verbatim}

@@

\begin{verbatim}
C4 factor: 1.11 
\end{verbatim}

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6072539 & 129628 \\
\end{longtable}

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-31} \end{center}

@@

\begin{verbatim}
2024-04-11 09:51:15.2 athan@sagan GHI_enh_02_ID_CE_highAOD.R 32.426616 mins
\end{verbatim}
